A Survey on Ordered Binary Decision Diagrams

### 2015-09-10 paper.tex
Finish representation basics introduction

\textit{Binary decision diagrams} (\textit{BDDs}) have been well studied since
Lee~\cite{LEE59} and especially Akers~\cite{AKERS78} introduced them. BDDs
represent a Boolean function $f$ as an acyclic, directed graph (DAG). Nodes
represent variables and have one incoming and two outgoing edges, each of which
denotes the variable evaluates to 0 (left) or 1 (right), respectively. Whenever
the result of $f$ is fixed, an edge points to one of the constant functions
\textbf{0} or \textbf{1}. To evaluate $f$ for a given variable assignment, one
just follows the path for the respective variable values. As soon as the path
ends up in a constant, i.e. \textbf{0} or \textbf{1}, this is the result of the
variable assignment. Akers~\cite{AKERS78} already provided some techniques to
simplify the BDD representation such as combining equivalent nodes.

\begin{figure}[ht]
    \centering
    \subfigure[BDD \newline $f=(A \land B) \lor (B \land C)$.]{
        \includestandalone[height = 3cm]{figs/bdd}
        \label{fig:bdd}
    }
    \hskip1cm
    \subfigure[OBDD \newline $f=(A \land B) \lor (B \land C)$.]{
        \includestandalone[height = 3cm]{figs/obdd}
        \label{fig:obdd}
    }
\end{figure}

@@

\subsection{Reducing and Ordering BDDs}
\label{subsec:reducing-and-ordering-bdds}

@@

>>>>

\textit{Binary decision diagrams} (\textit{BDDs}) have been well studied since
Lee~\cite{LEE59} and especially Akers~\cite{AKERS78} introduced them. BDDs
represent a Boolean function $f$ as an acyclic, directed graph (DAG). Nodes
represent variables and have one incoming and two outgoing edges, each of which
denotes the variable evaluates to 0 (left) or 1 (right), respectively. Whenever
the result of $f$ is fixed, an edge points to one of the constant functions
\textbf{0} or \textbf{1}. To evaluate $f$ for a given variable assignment, one
just follows the path for the respective variable values. As soon as the path
ends up in a constant, i.e. \textbf{0} or \textbf{1}, this is the result of the
corresponding variable assignment. Akers~\cite{AKERS78} already provided some
techniques to simplify the BDD representation such as combining equivalent nodes.

Figure~\ref{fig:bdd} shows an example of a BDD representing the Boolean function
$f=(A \land B) \lor (B \land C)$. To simplify the graphs, the diagram style of
Bryant~\cite{BRYANT92} is reused, i.e. edge labels are skipped. Instead dashed
and solid lines are used to represent the value of the decision variable to be 0
and 1, respectively. This diagram style is used throughout this paper.

\begin{figure}[ht]
    \centering
    \subfigure[BDD]{
        \includestandalone[height = 3cm]{figs/bdd}
        \label{fig:bdd}
    }
    \hskip1cm
    \subfigure[OBDD]{
        \includestandalone[height = 3cm]{figs/obdd}
        \label{fig:obdd}
    }
    \caption{BDD and OBDD of $f=(A \land B) \lor (B \land C)$.}
\end{figure}

However, Bryant~\cite{BRYANT86} introduced some restrictions concerning the
ordering of the so-called \textit{decision variables} represented by the vertices
of the BDD. Furthermore, Bryant\cite{BRYANT86} was able to derive a reduced
representation of BDDs providing the DAG in a canonical form. The following two
subsections cover the details.

@@

\subsection{From BDDs to OBDDs}
\label{subsec:from-bdds-to-obdds}

@@

\begin{figure}[ht]
    \centering
    \includestandalone[height = 3cm]{figs/min-obdd}
    \label{fig:min-obdd}
    \caption{Minimized OBDD (optimal).}
\end{figure}
\tbr
